Large scale agile transformations: A literature review

### 2013-01-23 tex/article.tex
Results

\subsection{Overview of agile methods used}

\begin{table}[h]
    \begin{tabular}{ l@{ \hskip 0.4cm } l }
        \toprule
        Agile method    & Reported in number of studies   \\ \midrule
        Scrum           & 18 \\ 
        XP              & 7 \\
        Lean            & 5 \\
        Tailoring and combining methods & 9  (indirect mentionings not counted) \\
        \bottomrule
    \end{tabular}
    \caption{Reported use of agile methods}
    \label{table:practices}
\end{table}

\subsection{Motivations for transformation}

@@

        \raggedright\rule{0pt}{0.4cm}Lack of resources  &
            Lack or training, insufficient resources for coaching \\
        \bottomrule
    \end{tabular}
    \caption{Typical challenges encountered in studies}
    \label{table:challenge}
\end{table}

>>>>

Most of the primary studies stated which agile methods were in use. The most
commonly reported methods are listed in Table \ref{table:methods}, of which
Scrum was the most popular single method. An important observation is that
tailoring of methods was very common. The use of tailoring can be considered
relating particularly to large scale, as the core of agile methods give very
little advice on interfacing with various units present in a large organization.

\begin{table}[h]
    \begin{tabular}{ l@{ \hskip 0.4cm } l }
        \toprule
        Agile method    & Reported in number of studies   \\ \midrule
        Scrum           & 18 \\ 
        XP              & 7 \\
        Lean            & 5 \\
        Tailoring and combining methods & 9  (indirect mentionings not counted) \\
        \bottomrule
    \end{tabular}
    \caption{Reported use of agile methods}
    \label{table:methods}
\end{table}

The reasons to initiate a change fell into three categories, as summarized in
Table \ref{table:motivations}. The primary reasons for change was a strategical
need to improve the performance of the organization, such as shorten the time to
market for new features. In many cases the change was started when management
acknowledged problems in the current way of working.

@@

        \raggedright\rule{0pt}{0.4cm}Lack of resources  &
            Lack or training, insufficient resources for coaching \\
        \bottomrule
    \end{tabular}
    \caption{Typical challenges encountered in studies}
    \label{table:challenges}
\end{table}
